---
output: github_document
---

# Fars Package

The goal of fars is the data from the US National Highway Traffic Safety Administration's [Fatality Analysis Reporting System](https://www.nhtsa.gov/Data/Fatality-Analysis-Reporting-System-(FARS)), which is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes. 

## Installation

You can install fars from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("BreizhZut/Fars")
```

Dependencies

```{r depen_lib, message=FALSE}
library(dplyr)
library(readr)
library(tidyr)
library(magrittr)
library(maps)
```

Loading the library

```{r lib, message=FALSE}
library(fars)
```

## Example: reading a file

In oder to work properly one need to check the data location.

```{r setdir}
fars_dir = file.path("tests","data")
list.files(fars_dir)
```

This packaque contains a function to build standard names

```{r filename}
file2013 <- make_filename(2013)
file2013
```

The `fars_read` function reads the file, the optionnal argument `fars_path` unables the user to specify the directory cotainong the data.

```{r data}
library(knitr)
data2013 <- fars_read(file2013,fars_path=fars_dir)
kable(head(data2013))
```


[![Build Status](https://travis-ci.org/BreizhZut/Fars.svg?branch=master)](https://travis-ci.org/BreizhZut/Fars)
