---
title: "Exploring the evolution of accidents per month accross multiple years"
author: "D Tweed"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Exploring the evolution of accidents per month accross multiple years}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Problem

The FARS database is contained in mutltiple files, ne per year actually.

```{r setdir}
fars_dir = file.path("..","..","data")
list.files(fars_dir)
```
What we aim to do now is to count the number of incidents per month for this we need:
1. Select the file corresponding to the year range we wan't to explore
1. Read each file and add its content to a data.frame
1. Aggregate per month and count the number of rows


## Fars package implementations

```{r}
library(fars)
acc_month <- fars_read_years(2013:2015,path= fars_dir)
acc_month
```

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
