---
title: "Exploring the evolution of accidents per month accross multiple years"
author: "D. Tweed"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Exploring the evolution of accidents per month accross multiple years}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Problem

The FARS database is contained in multiple files, one per year actually.

```{r setdir}
fars_dir = file.path("..","tests","data")
list.files(fars_dir)
```
What we aim to do now is to count the number of incidents per month for this we need:
1. Select the file corresponding to the year range we wan't to explore
1. Read each file and add its content to a data.frame
1. Aggregate per month and count the number of rows


## Fars package implementations

Loading dependancies

```{r depen_lib, message=FALSE}
library(dplyr)
library(readr)
library(tidyr)
library(magrittr)
library(maps)
library(knitr)
```

Loading the library

```{r lib, message=FALSE}
library(fars)
```

```{r read_years}
list_data <- fars_read_years(2012:2015,fars_path=fars_dir)
```

The warning indiate we have a missing file for which the output is `NULL`
```{r r2012}
list_data[[1]]
```

For the remaining entries 
```{r r2013}
kable(head(list_data[[2]]))
```
```{r r2014}
kable(head(list_data[[3]]))
```
```{r r2015}
kable(head(list_data[[4]]))
```

This function is used within the `fars_summarize_years` function that aggrage the data per month and year. 

```{r year_sum}
data_years <- fars_summarize_years(2013:2015,fars_dir)
kable(data_years)
```

## Alternative grouping and plotting

Finally we can display the result 

```{r fig,fig.width=8,fig.height=4}
library(ggplot2)

data_years <- list_data %>% bind_rows() %>% 
    select(month=MONTH,year=year) %>%
    group_by(year, month) %>%
    summarize(n = dplyr::n())

ggplot(data_years,aes(x=month,y=n,color=as.factor(year))) +
    geom_line() +
    scale_colour_discrete(name  ="Year") +
    scale_x_continuous(name="Month",breaks=1:12,labels=month.name) +
    scale_y_continuous(name="Nb of accidents") +
    theme_bw()+
    theme(legend.justification=c(0,1),legend.position=c(0.05, 0.95))
```
