---
title: "Displaying FARS location for a state"
author: "D. Tweed"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Displaying FARS location for a state}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Problem

Display the location of accidents for a specific year and state

First let set up the directory contianing he file

```{r setdir}
fars_dir = file.path("..","tests","data")
list.files(fars_dir)
```


## Fars package implementations

Loading dependancies

```{r depen_lib, message=FALSE}
library(dplyr)
library(readr)
library(tidyr)
library(magrittr)
library(maps)
library(knitr)
```

Loading the library

```{r lib, message=FALSE}
library(fars)
```

In the fars dataset numbers are used for states. We can find the correspondance with variable `state.name`

```{r state}
kable(data.frame(num=1:10,state=state.name[1:10]))
```

```{r }
data2014 <- fars_read(make_filename(2014),fars_dir)
data2014 %>% group_by(STATE) %>% summarize(n=n()) %>%     mutate(state_name=state.name[STATE]) %>% arrange(desc(n))
    
```

Now we are using the `fars_map_state` function to display the localisation of accident in California in 2014. 
We may notice that California correspond to state 6 instead of 5.

```{r }
library(ggplot2)
fars_map_state(6,2013,fars_dir)
```

